\ttitle

### 2014-01-14 Chapters/Chapter7.tex
Added plots for chapter 6
WIP: chapter 5 and 6

In this research we have applied \gls{occ} methods to accelerometer data, recorded during the performance of various human activities, in order to create a temporal segmentation of those recordings.
The goal was to find the change points between activities, assuming that it will aid better understanding of the sensor values.
To do so, we used the \gls{svdd} algorithm by Tax~\cite{tax1999support}, following the method of applying it to a sliding window of data, as done by Camci~\cite{camci2010change}.
Instead of using both the information whether a new data point is an outlier and the radius of the hypersphere to indicate change, we only used the latter model properties.
The increase of the radius of the constructed hypersphere, which encloses the data objects and increases with heterogeneous segments of data, is extracted and used for indication of change.

In the following section we will further discuss the proposed method for temporal segmentation of inertial sensor signals from human activities.
Our main findings and contributions are discussed in \Cref{sec:main_findings}.
The limitations of our method and research is subject of \Cref{sec:limitations}.
These two sections are followed by our suggestions for future research.
\Cref{sec:final_remarks} is the final section of this thesis.

\section{What is done}
The scope of this research was the temporal segmentation of recordings obtained from human activities.
This was performed in the wider context of activity classification.
Currently, many algorithms obtain an implicit segmentation as a side-effect of direct activity classification.
In this research the primary goal was finding a temporal segmentation, which is assumed to be able to aid the classification step.
This problem is reduced to finding change points in temporal data sets originating from inertial sensors.

@@

In this research we have applied the method by Camci~\cite{camci2010change} to data from inertial sensors, recorded by smartphones.
We have used the accelerometer data for measurement of speed, the gyroscope data for measurement of rotation, and the magnetometer to measure the direction and orientation of the performed activities.
The proposed method, as discussed in \Cref{Chapter4}, reduces this 9-dimensional signal to a single property, obtained from the constructed model, which can be interpreted to indicate change.

@@

\section{Main findings / Contributions}\label{sec:main_findings}
\TODO{Vraag aan Anne: wat is een goede titel voor deze section? Of moeten we Findings en Contributions splitsen?}
While temporal segmentation of time series data is not uncommon, the application to inertial signals is currently not under much research attention.
For other contexts it has been applied, such as motion tracking \cite{barbivc2004segmenting,li2007segmentation}.
In the context of human activities the segmentation obtained from inertial sensor signals is often an implicit result of classification.

@@

\TODO{Toevoegen: samenvatting van resultaten uit \Cref{Chapter6}: de subjectieve waarnemingen?}

@@

In that same line, we have encountered situations in which the exclusion of some sensors, \eg the accelerometer, yields better results.
This occurs mainly in situations where a rotation is part of the change (\eg walking around a corner).
Thus depending on the desired granularity of the segmentation, it can be beneficial to disregard some of the time series data.
Determining (dynamically) which sensors should be, and which should not be, used in the model construction phase (known as \emph{feature selection}) could be a subject of further research.

@@

\section{Final words}\label{sec:final_remarks}
In this research we have constructed a method to create a temporal segmentation of inertial sensor time series data, originating from performed human activities.
To this end we have applied \gls{occ} and \gls{oc-svm} based method to our own recorded data sets.
We followed the approach by Camci~\cite{camci2010change} and used the theory and implementation of \gls{svdd} by Tax~\cite{tax2001one,Ddtools2013}.
Although the performance of the method heavily depends on user set parameters, the results are promising.
We believe that the temporal segmentation of time series data can aid the process of activity classification, which is a logical follow-up on this research.
\TODO{Hier nog meer samenvatten?}

>>>>

In this research we have applied \gls{occ} methods to accelerometer data, recorded during the performance of various human activities, in order to create a temporal segmentation of those recordings.
The goal was to find the change points between activities, assuming that it will aid our understanding of the sensor values.
To do so, we used the \gls{svdd} algorithm by Tax~\cite{tax1999support}, following the method of applying it to a sliding window of data, as done by Camci~\cite{camci2010change}.
Instead of using both the information whether a new data point is an outlier and the radius of the hypersphere to indicate change, we only used the latter model properties.
The increase of the radius of the constructed hypersphere, which encloses the data objects and increases with heterogeneous segments of data, is extracted and used for indication of change.

In the following section we will further discuss the proposed method for temporal segmentation of inertial sensor signals from human activities.
Our main findings and contributions are discussed in \Cref{sec:main_findings}.
The limitations of our method and research is subject of \Cref{sec:limitations}.
\Cref{sec:further_research} provides suggestions for future research.
\Cref{sec:final_remarks} is the final section of this thesis.

\section{What is done?}
The goal of this research was to find a temporal segmentation of recordings obtained from human activities.
This was performed in the wider context of activity classification.
Currently, many algorithms obtain an implicit segmentation as a side-effect of direct activity classification.
In this research the primary goal was finding a temporal segmentation, which is assumed to be able to aid the classification step.
This problem is reduced to finding change points in temporal data sets originating from inertial sensors.

@@

In this research we have applied the method by Camci~\cite{camci2010change} to data from inertial sensors, recorded by smartphones.
We have used the accelerometer data for measurement of speed, the gyroscope data for measurement of rotation, and the magnetometer to measure the direction and orientation of the performed activities.
The proposed method, as discussed in \Cref{Chapter4}, reduces a high dimensional signal to a single property, obtained from the constructed model, which can be interpreted to indicate change.

@@

\section{Contributions}\label{sec:main_findings}
While temporal segmentation of time series data is not uncommon, the application to inertial signals is currently not under much research attention.
For other contexts it has been applied, such as motion tracking \cite{barbivc2004segmenting,li2007segmentation}.
In the context of human activities the segmentation obtained from inertial sensor signals is often an implicit result of classification.

@@

\TODO{Vraag aan Anne: toevoegen samenvatting van resultaten uit \Cref{Chapter6}: de subjectieve waarnemingen?}

@@

In that same line, we have encountered situations in which the exclusion of some sensors, \eg the accelerometer, yields better results.
This occurs mainly in situations where a rotation is part of the change (\eg walking around a corner).
Thus depending on the desired granularity of the segmentation, it can be beneficial to discard some of the time series data.
Determining (dynamically) which sensors should be, and which should not be, used in the model construction phase (known as \emph{feature selection}) could be a subject of further research.

@@

\section{Final words}\label{sec:final_remarks}
In this research we have constructed a method to create a temporal segmentation of inertial sensor time series data, originating from performed human activities.
To this end we have applied \gls{occ} and \gls{oc-svm} based method to our own recorded data sets.
We followed the approach by Camci~\cite{camci2010change} and used the theory and implementation of \gls{svdd} by Tax~\cite{tax2001one,Ddtools2013}.
Although the performance of the method heavily depends on user set parameters, the results are promising.
We believe that the temporal segmentation of time series data can aid the process of activity classification, which is a logical follow-up on this research.
\TODO{Vraag aan Anne: Hier nog meer samenvatten? Wat is een goede uitsmijter?}
